Understanding Parameterized Quantum Circuit Learning for Quantum Chemical Applications

### 2025-03-19 manuscript/main.tex
spring cleaning

sixteen qubit \ref{fig:16BSE_heatplots} \ref{fig:16BSE_boxplots}
removed the really bad ones from five qubit
best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
Best encoder on average train R$^{2}$/test R$^{2}$
Best ansatz on average train R$^{2}$/test R$^{2}$
A2_Hadamard

>>>>

sixteen qubit \ref{fig:16BSE_heatplots} \ref{fig:16BSE_boxplots}
removed the really bad ones from five qubit
best encoder-ansatz pair: train R$^{2}$/test R$^{2}$
Best encoder on average train R$^{2}$/test R$^{2}$
Best ansatz on average train R$^{2}$/test R$^{2}$
A2{\_}Hadamard
